Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-20 report/report.tex
Update todo
Include way widths in report
Update Todo
Add table for post-correction data

% TODAY
% TODO: way-collisions.py: Progress bar
% TODO: Quote Todor's paper for geodata import services and current state of the field
% TODO: RELATED WORK, mention current sources (Haklay, Fan)
% TODO: ANALYSIS SECTION, figure out what to write
% TODO: Figure of street, before correction

% TOMORROW
% TODO: Proof read entire report
% TODO: Plan collision correction
% TODO: Collision correction run
% TODO: Table for collision correction data in report

% TUESDAY
% TODO: Figure of street, after correction
% TODO: Write analysis section
% TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?
% TODO: Start large data run, way collision

@@

@@

>>>>

% MONDAY
% TODO: Quote Todor's paper for geodata import services and current state of the field
% TODO: RELATED WORK, mention current sources (Haklay, Fan)
% TODO: ANALYSIS SECTION, figure out what to write

% TODO: Collision correction: Fix collisions by relaxing both feature_1 and feature_2

% TUESDAY
% TODO: Collision correction: Edit edge distance function to factor in width of the other path
% TODO: Collision correction run
% TODO: Figure of street, before correction, after correction
% TODO: Table for collision correction data in report

% TODO: Write analysis section
% TODO: Dig deeper in the SLU dataset, how can one find the method of aquisition for Stockholm buildings, and its precision?

% WEDNESDAY
% TODO: Proof read entire report
% TODO: Start large data run, way collision

@@

Subsequent visual measurements of a few key locations in the Stockholm area revealed the following minimum way widths:
\begin{table}[H]
\begin{tabular}{lllll}
                  & Footpath & Residential & Secondary & Primary \\
    Minimum width & 2.0 m    & 6.0 m       & 6.5 m     & 8.0 m   \\
    Maximum width & 5.0 m    & 9.0 m       & 10.0 m    & 16.0 m
\end{tabular}
\end{table}

@@

After collision correction:

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & & & & \\
    Nodes, total            & & & & \\
    Edge length, total      & m & m & m & m \\
    Features, colliding     & & & & \\
    Nodes, colliding        & & & & \\
    Edge length, colliding  & m & m & m & m \\
    Features, percent       & \% & \% & \% & \% \\
    Nodes, percent          & \% & \% & \% & \% \\
    Edge length, percent    & \% & \% & \% & \%
